\documentclass[11pt]{article}
\usepackage{mgates-letter}
\definecolor{dark_blue} {rgb}{0., 0., 0.65}
\usepackage{makecell}
\usepackage[
backend=biber,
style=numeric,
citestyle=numeric,
maxcitenames=10,
maxnames=10,
%entrykey=false,
%annotation=false,
url=false
]{biblatex}

\usepackage{second-year-phd-report}
\addbibresource{references.bib}

\begin{document}
\sloppy
\begin{center}
	{{
		\Large{
			\textsc{PhD Programme in Computer Science and Engineering \\ 
			\vspace{4mm}
			Cycle XXXVIII}
			}
	}} 
	\rule[0.1cm]{\textwidth}{0.1mm}
	\rule[0.4cm]{\textwidth}{0.6mm}
\end{center}

\begin{center}
	{\LARGE{Symbolic Knowledge Injection \& Extraction for Autonomous Learning}} \\
	\vspace{4mm}
	{\large{PhD Year II -- Report}} 
	\vspace{4mm}
\end{center}
\vspace{8mm}
\par
\noindent
\begin{minipage}[t]{0.47\textwidth}

{\large{Commission: \\\bf
Prof. Andrea Omicini \\
Prof. Enrico Denti \\
Prof. Giovanni Pau}
}
\end{minipage}
\hfill
\begin{minipage}[t]{0.47\textwidth}
	\raggedleft
	{
		\large{PhD Student: \\\bf Matteo Magnini}
	}
\end{minipage}
\vspace{10mm}

{
	\raggedright
	\rule[0.1cm]{\textwidth}{0.6mm}
	\rule[0.5cm]{\textwidth}{0.1mm}
}

\newcommand{\rev}[1]{{
	%\color{red}
	#1
	}}
\section{Introduction}
During the second year of my PhD, I have been working on several tasks, including research publications, teaching, visiting, participation in conferences, supervision of graduating students, and PhD courses.
%
In this report, I will provide a brief -- yet exhausting -- overview of the activities I have carried out during the second year.


\section{Research}

%
\subsection{Period Abroad}
I have moved to Norway for a period of 3 months, from the 5th of March to the 8th of June 2024.
%
I was hosted by Prof.~Ana Ozaki at the University of Oslo, where I had the opportunity to work with her along with her research group.
%
During this period, I have been working on the development of a new tool for the learning of ontologies by means of \ac{LLM}.
%
In particular, the work started from the ExactLearner tool\footnote{\url{https://github.com/ExactLearner/ExactLearner}}, and it has been extended to support the learning of ontologies from text\footnote{\url{https://github.com/MatteoMagnini/ExactLearner}}.
%
One paper has been already published~\cite{DBLP:conf/dlog/MagniniOS24}, and a more comprehensive work is currently undergoing.


\section{Talks}


\section{International Conference Activities}


\section{Teaching}
\begin{enumerate}
	\item Teaching assistant @ Distributed System 2023/2024, Ingegneria e Scienze Informatiche LM, 24 ore
	\item Teaching assistant @ Distributed System 2024/2025, Ingegneria e Scienze Informatiche LM, 24 ore
\end{enumerate}


\section{Courses and School}
\label{sec:courses-and-school}
%
In \Cref{tab:courses-and-school}, I report the courses and schools I have attended during the first and second year of the PhD.
%
The courses of the first and second year are divided by a horizontal line to highlight the two different years.
%
In total, I have attended 6 courses and 1 school during the first year, and 4 courses and 1 school during the second year.
%
The total amount of proposed CFUs with exam is 20, while the total amount of proposed CFUs without exam is 6.
%
\begin{table}[H]
	\resizebox{\textwidth}{!}{%
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Professor & Course & Kind & Credits & Period & Exam \\ \hline
		Mirko Musolesi & \makecell{Comparative Introduction to Deep Learning Frameworks:\\ TensorFlow,PyTorch and Jax} & PhD Course & \makecell{6 hours \\ 1 proposed credits} & \makecell{Nov. \\ 2022} & Done \\ \hline
		Flavia Esposito & \makecell{Low-rank Approaches for Data Analysis:\\ Models, Numerical Methods and Applications} & PhD Course & \makecell{10 hours \\ 2 proposed credits} & \makecell{Jan. \\ 2023} & Done \\ \hline
		Paolo Torroni & \makecell{How to Write and Publish a Research Paper\\ in Computer Science and Engineering} & PhD Course & \makecell{10 hours \\ 2 proposed credits} & \makecell{May \\ 2023} & Done \\ \hline
		Matteo Francia & \makecell{Data Platforms and Artificial Intelligence:\\ Challenges and Applications} & PhD Course & \makecell{10 hours \\ 2 proposed credits} & \makecell{Jun. \\ 2023} & Not Done \\ \hline
		 & \makecell{10th International Gran Canaria School on Deep Learning} & School & \makecell{40 hours \\ 4 proposed credits} & \makecell{Jul. \\ 2023} & Done \\ \hline
		Danilo Pianini & \makecell{Devops meets scientific research} & PhD Course & \makecell{20 hours \\ 4 proposed credits} & \makecell{Jun. - Jul. \\ 2023} & Done \\ \hline
		\hline
		Giovanni Ciatto & \makecell{Multi-platform Programming \\for Research-Oriented Software} & PhD Course & \makecell{10 hours \\ 2 proposed credits} & \makecell{Oct. - Nov. \\ 2023} & Not done \\ \hline
		Mirko Musolesi & \makecell{An Introduction to Reinforcement Learning} & PhD Course & \makecell{16 hours \\ 3 proposed credits} & \makecell{Oct. - Nov. \\ 2023} & Done \\ \hline
		Fabio Pierazzi & \makecell{Risk Assessment of Machine Learning\\ for Cybersecurity} & PhD Course & \makecell{20 hours \\ 4 proposed credits} & \makecell{Apr. \\ 2024} & Done \\ \hline
		Andrea Roli & \makecell{Introduction to complex systems science} & PhD Course & \makecell{10 hours \\ 2 proposed credits} & \makecell{Jun. - Jul. \\ 2024} & Not done \\ \hline
	\end{tabular}
	}
	\caption{Courses and Schools attended during the second year of the PhD.}
	\label{tab:courses-and-school}
\end{table}

\section{Papers}

\subsection{Published}

\begin{itemize}
    \item \cite{DBLP:conf/woa/RafanelliMACO24}
	%\\{\footnotesize\textbf{Abstract:}~\citefield{DBLP:conf/woa/RafanelliMACO24}{abstract}}
    %
	\item \cite{DBLP:conf/percom/MontagnaAFPKUM24}
	%\\{\footnotesize\textbf{Abstract:}~\citefield{DBLP:conf/percom/MontagnaAFPKUM24}{abstract}}
	%
	\item \cite{DBLP:conf/dlog/MagniniOS24}
	%\\{\footnotesize\textbf{Abstract:}~\citefield{DBLP:conf/dlog/MagniniOS24}{abstract}}
	%
	\item \cite{DBLP:journals/csur/CiattoSAMO24}
	%\\{\footnotesize\textbf{Abstract:}~\citefield{DBLP:journals/csur/CiattoSAMO24}{abstract}}
\end{itemize}

\subsection{Accepted}

\begin{itemize}
	\item dummy
\end{itemize}

\subsection{In Peer Review}

\begin{itemize}
	\item dummy
\end{itemize}

\section{References}
\printbibliography[heading=none]

\end{document}
